Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling

### 2025-01-03 lit.tex
Edits before format review

Others adopted extensible software frameworks for developing numerical solvers
to develop multiphysics reactor analysis software. Examples of these software
frameworks include the commercial COMSOL
Multiphysics\textsuperscript{\textregistered} software
\cite{comsol_ab_comsol_nodate}, the aforementioned open-source CFD toolbox
OpenFOAM, and the open-source finite-element
framework \gls{MOOSE} \cite{giudicelli_30_2024}. Researchers at
\gls{PoliMi} developed an \gls{MSR} simulation tool in COMSOL and
modeled the \gls{MSBR} as a single axisymmetric fuel channel with a uniform
flow profile \cite{cammi_multi-physics_2011}, followed by the \gls{MSRE} core
also as a single axisymmetric fuel channel with parabola-shaped laminar flow
\cite{cammi_dimensional_2012}. They later expanded on their approach by
modeling the \gls{MSRE} upper plenum, downcomer and lower plenum, primary heat
exchanger, and secondary heat exchanger as 0D systems (lumped-parameter model)
and substituting the 2-D fuel channel with a 3-D fuel channel which more closely
resembled the actual fuel channels in the \gls{MSRE}
\cite{zanetti_geometric_2015}. Other than the \gls{MSRE}, they also modeled the
\gls{MSFR} in a later publication \cite{fiorina_modelling_2014}, which also featured \gls{TUD}'s
DALTON-HEAT coupled multiphysics tool.

@@

Eddy viscosity models, which comprise the most widely used turbulence models
in use today \cite{rodi_turbulence_2017}, operate on the eddy viscosity
hypothesis which states that the Reynolds stresses in the \gls{RANS} equations
are given by:
%
\begin{align}
    \langle u_iu_j \rangle =& \frac{2}{3}k \delta_{ij} - \nu_T \left(
    \frac{\partial U_i}{\partial x_j} + \frac{\partial U_j}{\partial x_i}
    \right)
    \shortintertext{where}
    k =& \mbox{ mean turbulent kinetic energy,} \nonumber \\
    \delta_{ij} =& \mbox{ Kronecker delta,} \nonumber \\
    \nu_T =& \mbox{ eddy viscosity.} \nonumber \\
\end{align}

@@

\glspl{RSM} directly compute the individual components $\langle u_i u_j
\rangle$ of the Reynolds stress tensor instead of approximating it with a
single, isotropic eddy viscosity term. Consequently, \glspl{RSM} provide
more realistic predictions for flows with significant rotational motion and
sudden changes in the mean strain rate, albeit at greater computational
expense, compared to the one- and two-equation models
\cite{wilcox_turbulence_2006}. More minor improvements are observed in modeling
free shear and backward-facing step flows \cite{wilcox_turbulence_2006}.

@@

There is a lack of research interest in methods for improving control rod modeling in
\glspl{MSR}.
The self-regulating nature and low excess reactivity of \glspl{MSR} reduce or even eliminate the
need for control rods \cite{dolan_1_2017}. This characteristic arises from the strongly negative
temperature reactivity feedback and the strong coupling to flow and heat removal rates. \gls{MSR}
reactor designers rely on these passive mechanisms for reactor safety. In addition, they propose
load-following operation by adjusting pump speeds and the temperature of the intermediate coolant
loop. Laureau et al.\ \cite{laureau_transient_2017} demonstrated simple power ramp-up and ramp-down
with the \gls{MSFR} by varying the temperature of the secondary coolant. \gls{MSR}
designs with no control rods include the fast-spectrum \gls{MSFR} and TerraPower's \gls{MCFR}
\cite{terrapower_terrapower_2021}. However, \gls{MSR} power control schemes which rely heavily on
these mechanisms may not be suitable for all accident scenarios. Control rod insertion provides
an important additional means of reactor shut-down without draining the fuel salt, which
complicates reactor restart procedures. We also note that thermal \gls{MSR} designs like the
\gls{MSRE}, \gls{MSBR}, and TMSR-LF1 designs still include control rods as essential components,
partly due to their less negative temperature reactivity feedback coefficients
compared to their fast-spectrum counterparts. Thus, the existing literature on control rod modeling
in \glspl{MSR} are based on thermal-spectrum \glspl{MSR}.

Few \gls{MSR} multiphysics studies explicitly include control rods in their models. For instance,
for the \gls{MSRE} pump start-up and coast-down experiments at \gls{ORNL} which involved control
rod movement, most numerical studies simulate the reactivity effects of the control rods by scaling
the neutron source term by the neutron multiplication factor to keep their reactor model at
criticality \cite{delpech_benchmark_2003, krepel_dyn3d-msr_2007}. Some studies include control rod
models in their steady-state calculations. However, they resort to neutron source term scaling for
the transient calculations due to the inaccuracy of neutron diffusion, $P_1$, and $SP_N$ methods in
highly neutron absorbing regions \cite{kophazi_development_2009, jaradat_development_2021,
yang_development_2022}. Kophazi et al.\ \cite{kophazi_development_2009} modeled annular control rods
as homogenized hexahedrons in their 3-D Cartesian geometry of the \gls{MSRE}. They
homogenized fuel and graphite regions in the rest of the reactor model, as mentioned in Subsection
\ref{sec:msr-tools}. To reduce errors introduced by the neutron diffusion method, they imposed
simple albedo boundary conditions for the thermal neutron group. Jaradat et al.\
\cite{jaradat_development_2021} and Yang et al.\ \cite{yang_development_2022} modeled the
\gls{MSRE} control rods as homogenized wedges in their R-$\theta$-Z mesh due to the constraints of
the nodal neutronics solver. Cui et al.\ \cite{cui_development_2021} also homogenized the control
rods as regular hexahedral nodes in accordance with their nodal solver in Cartesian geometry. A
disadvantage of homogenization-based methods is that it removes some of the heterogeneity in the
flux and temperature. The heterogeneous temperature distribution is especially important in
\glspl{MSR} due to the combined fuel-coolant and the positive temperature reactivity feedback
observed in graphite under certain conditions \cite{mathieu_thorium_2006}.

@@

High-fidelity neutron transport methods fall under two general categories: stochastic Monte Carlo
methods and deterministic methods. Monte Carlo methods involve simulating a finite number of
neutron histories. Randomly generated numbers determine the outcome of various probabilistic events
such as travel distances between particle collisions, types of collisions, and scattering angles in
each history until a neutron capture event terminates it. Deterministic methods for neutron
transport, such as the discrete ordinates $S_N$ and spherical harmonics $P_N$ methods, solve the
\gls{BTE} for neutron transport with some approximations for handling the angular and energy
dependence. The \gls{BTE} for neutron transport is given as:
%
\begin{align}
  \frac{1}{v(E)} \frac{\partial}{\partial t} \Psi(\vec{r},E,\hat{\Omega},&t) + \hat{\Omega}\cdot
  \nabla\Psi(\vec{r},E,\hat{\Omega},t) + \Sigma_t(\vec{r},E,t)\Psi(\vec{r},E,\hat{\Omega},t) 
  \nonumber \\
  - \int^\infty_0 dE'& \int_{4\pi} d\hat{\Omega}' \Sigma_s(\vec{r},E'\rightarrow E,\hat{\Omega}'
  \rightarrow \hat{\Omega},t) \Psi(\vec{r},E',\hat{\Omega}',t) \nonumber \\
  =& \frac{\chi(E)}{4\pi}
  \int^\infty_0 dE' \int_{4\pi} d\hat{\Omega}' \nu\Sigma_f(\vec{r},E',t) \Psi(\vec{r},E',
  \hat{\Omega}',t)+S(\vec{r},E,\hat{\Omega},t) \label{eq:bte}
  \shortintertext{where}
  v(E) =& \mbox{ neutron velocity,} \nonumber \\
  \Psi(\vec{r},E,\hat{\Omega},t) =& \mbox{ neutron angular flux,} \nonumber \\
  \vec{r} =& \mbox{ spatial coordinates,} \nonumber \\
  E =& \mbox{ neutron energy,} \nonumber \\
  \hat{\Omega} =& \mbox{ direction of neutron travel,} \nonumber \\
  t =& \mbox{ time,} \nonumber \\
  \Sigma_t(\vec{r},E,t) =& \mbox{ macroscopic total cross section,} \nonumber \\
  \Sigma_s(\vec{r},E'\rightarrow E,\hat{\Omega}'\rightarrow \hat{\Omega},t) =&
  \mbox{ macroscopic scattering cross section,} \nonumber \\
  \chi(E) =& \mbox{ fission neutron spectrum,} \nonumber \\
  \nu =& \mbox{ number of neutrons produced per fission reaction,} \nonumber \\
  \Sigma_f(\vec{r},E',t) =& \mbox{ macroscopic fission cross section,} \nonumber \\
  S(\vec{r},E,\hat{\Omega}',t) =& \mbox{ external neutron source.} \nonumber
\end{align}

@@

Scherer \& Neef developed the \gls{MECS} \cite{scherer_determination_1976} to improve control rod
modeling in \gls{HTGR} with mesh-centered nodal diffusion methods. The \gls{MECS} involves running
a 1-D neutron transport calculation on a representative \textit{supercell} of the heterogeneous
absorber region and its vicinity. The supercell is a volume-preserved model of the absorber region
approximated from its cylindrical or Cartesian geometry in the diffusion calculation. The transport
calculation is typically performed using a fine group structure, fine spatial discretization, and
high-order angular discretization and scattering moments (e.g., $S_8$ method with $P_3$ scattering
matrix) \cite{fen_modelling_1992}. The calculated net neutron leakage rates from the transport
solver are matched with the calculated leakage rates from the diffusion solver according to an
analytic calculation to obtain equivalent diffusion coefficients or cross sections for the absorber
region. The diffusion coefficient formula for this analytic calculation depends on the solution
method of the diffusion solver. In the most widely used implementation of \gls{MECS} used in
conjunction with the mesh-centered diffusion code CITATION \cite{teuchert_vsop94_1994}, the
diffusion coefficient formula assumes there is only one inner mesh point in the absorber region as
using more inner mesh points dramatically increases the difficulty of finding the proper analytic
formula \cite{fen_modelling_1992}. Other macroscopic cross sections for the absorber region are
calculated using conventional group constant generation techniques from the transport solution
using the supercell average flux and reaction rates. To facilitate further discussion of the
\gls{MECS}, here is an example of applying the \gls{MECS} on a control rod in x-y geometry (Figure
\ref{fig:mecs-geometry}) in the CITATION code as provided by Fen et al.\ \cite{fen_modelling_1992}.
%
\begin{figure}[htb]
    \centering
    \includegraphics[width=.4\columnwidth]{mecs-geometry}
    \caption{Geometries of the absorber region and its vicinity in the supercell
      (top) and the diffusion solver mesh (bottom).
        The shaded and unshaded regions represent the homogenized absorber
        region and the adjacent non-absorber region, respectively.
        Retrieved from Fen et al.\ \cite{fen_modelling_1992}.}
    \label{fig:mecs-geometry}
\end{figure}

@@

As illustrated by the implementation in CITATION, \gls{MECS} requires considerable user input on
the supercell configuration to ensure that the leakage rates of the transport solution are
equivalent to the leakage rates of the subsequent diffusion solution. This procedure also places
some constraints on the location and size of the absorber node that can be inconsistent with the
nodalization of the rest of the reactor geometry \cite{ougouag_transport_2010}. \gls{MECS} is
incompatible with reactor geometries which contain control rods that are too close to each other
such that there is not enough distance in between to define neighboring nodes where
flux-equivalence is assumed. Lastly, \gls{MECS} is only applicable to coarse-mesh solvers and
homogenizes the control rod along with the adjacent material in its vicinity. Nevertheless,
\gls{MECS} has been widely used within the \gls{VSOP} suite of codes (which contains CITATION) for
\gls{HTGR} neutronic safety analyses
\cite{fen_modelling_1992, reitsma_evaluating_2003, mulder_neutronics_2020}.

@@

In doing so, the Ronen method provides pointwise corrections to the diffusion equation, overcoming
the small flux gradient limitation. Tomatis \& Dall'Osso \cite{tomatis_application_2011}
numerically implemented the Ronen method for a 1-D homogeneous slab with two energy groups and
isotropic scattering. Instead of using Eq. \ref{eq:ronen}, which showed instabilities near flat
flux regions where the denominator approaches zero, they calculated corrections to the diffusion
coefficients at cell interfaces using the difference between the transport- and diffusion-derived
currents as follows:
%
\begin{align}
  \delta D(x_{i+1/2},E) =& -\delta J(x_{i+1/2},E) \frac{(\Delta x_{i+1}+\Delta x_i)/2}{
  \phi(x_{i+1},E)+\phi(x_i,E)} \label{eq:tomatis}
  \shortintertext{where}
    x_i =& \mbox{ $i$-th spatial interval,} \nonumber \\
    \delta J(x,E) =& J_{tr}(x,E) - J_D(x,E), \nonumber \\
    \Delta x_i =& \mbox{ size of $i$-th spatial interval.} \nonumber
\end{align}

@@

As mentioned in Section \ref{sec:summary-nts-mtds}, coarse-mesh and nodal methods homogenize
heterogeneities in reactor geometries to reduce the computational costs of running full-core
simulations. Equivalence techniques which reduce spatial homogenization error are also effective
for accurately modeling the integral worths of control rods within fuel assemblies. The \gls{GET}
\cite{koebke_new_1980, smith_nodal_1983} and \gls{SPH} \cite{kavenoky_sph_1978,
hebert_consistent_1991} methods represent the most widely used equivalence methods for improving
the performance of diffusion calculations in homogenized \gls{LWR} models. Both methods involve
deriving additional homogenization parameters from single-assembly transport calculations with
reflective boundary conditions. Since the transport calculation step is already a prerequisite
for generating homogenized group constants, the equivalence methods are simple to implement and
impose reasonably small additional computational costs.

@@

The \gls{GET} and the \gls{SPH} methods are designed to preserve reaction rates at the assembly
level \cite{yamamoto_cell_2004}. Given that the \gls{SPH} method introduces only one correction
factor per cell, it only preserves the average net current across all surfaces as opposed
to the net current at each surface with \gls{GET}. Similarly, the isotropic nature of \gls{SPH}
factors leads to worse pin-power estimates near control rods and reflectors compared to \gls{GET}.
However, the \gls{SPH} method is simpler to implement in the diffusion solver as the \gls{SPH}
factors can be precombined with the cross sections to generate \gls{SPH}-corrected cross sections.
\gls{GET} requires diffusion solvers, which allow for flux discontinuities at the interfaces.
Furthermore, \gls{GET} requires more memory to store up to six discontinuity factors, one for each
mesh surface, in 3-D calculations.

@@

Lastly, there is a lack of research focus into robust techniques for accurate control rod modeling
for time-dependent \gls{MSR} analyses. Control rods induce highly anisotropic fluxes within
themselves and their vicinities that the neutron diffusion approximation cannot model accurately.
Inaccurate rod worth estimates subsequently affect transient reactor power and temperature
distribution calculations. Higher-fidelity neutron transport methods remain too computationally
expensive for time-dependent multiphysics \gls{MSR} simulations. However, transport-correction
techniques can be applied to augment neutron diffusion calculations in these regions. While few
have been applied to \gls{MSR} multiphysics simulations other than albedo boundary conditions,
various techniques have been proposed and implemented for other reactor types. Helpful information
may be gleaned from these techniques to improve control rod modeling in \glspl{MSR} with the
neutron diffusion method.

>>>>

Others adopted extensible software frameworks for developing numerical solvers
to develop multiphysics reactor analysis software. Examples of these software
frameworks include the commercial COMSOL
Multiphysics\textsuperscript{\textregistered} software
\cite{comsol_ab_comsol_nodate}, the aforementioned open-source CFD toolbox
OpenFOAM, and the open-source finite-element
framework \gls{MOOSE} \cite{giudicelli_30_2024}. Researchers at
\gls{PoliMi} developed an \gls{MSR} simulation tool in COMSOL and
modeled the \gls{MSBR} as a single axisymmetric fuel channel with a uniform
flow profile \cite{cammi_multi-physics_2011}, followed by the \gls{MSRE} core
also as a single axisymmetric fuel channel with parabola-shaped laminar flow
\cite{cammi_dimensional_2012}. They later expanded on their approach by
modeling the \gls{MSRE} upper plenum, downcomer and lower plenum, primary heat
exchanger, and secondary heat exchanger as 0D systems (lumped-parameter model)
and substituting the 2-D fuel channel with a 3-D fuel channel that more closely
resembled the actual fuel channels in the \gls{MSRE}
\cite{zanetti_geometric_2015}. Other than the \gls{MSRE}, they also modeled the
\gls{MSFR} in a later publication \cite{fiorina_modelling_2014}, which also featured \gls{TUD}'s
DALTON-HEAT coupled multiphysics tool.

@@

Eddy viscosity models, which comprise the most widely used turbulence models
in use today \cite{rodi_turbulence_2017}, operate on the eddy viscosity
hypothesis that states that the Reynolds stresses in the \gls{RANS} equations
are given by:
%
\begin{align}
    \langle u_iu_j \rangle =& \frac{2}{3}k \delta_{ij} - \nu_T \left(
    \frac{\partial U_i}{\partial x_j} + \frac{\partial U_j}{\partial x_i}
    \right)
    \shortintertext{where}
    k =& \mbox{ mean turbulent kinetic energy,} \nonumber \\
    \delta_{ij} =& \mbox{ Kronecker delta,} \nonumber \\
    \nu_T =& \mbox{ eddy viscosity.} \nonumber \\
\end{align}

@@

\glspl{RSM} directly compute the individual components $\langle u_i u_j
\rangle$ of the Reynolds stress tensor instead of approximating it with a
single, isotropic eddy viscosity term. Consequently, \glspl{RSM} provide
more realistic predictions for flows with significant rotational motion and
sudden changes in the mean strain rate, albeit at greater computational
expense, compared to the one- and two-equation models
\cite{wilcox_turbulence_2006}. More minor improvements are observed in modeling
free shear and backward-facing step flows.

@@

Research interest in methods for improving control rod modeling in \glspl{MSR} is subdued compared
to the focus on modeling other physical interactions in \glspl{MSR}.
The self-regulating nature and low excess reactivity of \glspl{MSR} reduce or even eliminate the
need for control rods \cite{dolan_1_2017}. This characteristic arises from the strongly negative
temperature reactivity feedback and the strong coupling to flow and heat removal rates. \gls{MSR}
reactor designers rely on these passive mechanisms for reactor safety. In addition, they propose
load-following operation by adjusting pump speeds and the temperature of the intermediate coolant
loop. Laureau et al.\ \cite{laureau_transient_2017} demonstrated simple power ramp-up and ramp-down
with the \gls{MSFR} by varying the temperature of the secondary coolant. \gls{MSR}
designs with no control rods include the fast-spectrum \gls{MSFR} and TerraPower's \gls{MCFR}
\cite{terrapower_terrapower_2021}. However, \gls{MSR} power control schemes that rely heavily on
these mechanisms may not be suitable for all accident scenarios. Control rod insertion provides
an important additional means of reactor shut-down without draining the fuel salt, which
complicates reactor restart procedures. We also note that thermal \gls{MSR} designs like the
\gls{MSRE}, \gls{MSBR}, and TMSR-LF1 designs still include control rods as essential components,
partly due to their less negative temperature reactivity feedback coefficients
compared to their fast-spectrum counterparts. Thus, the existing literature on control rod modeling
in \glspl{MSR} are based on thermal-spectrum \glspl{MSR}.

Few \gls{MSR} multiphysics studies explicitly include control rods in their models. For instance,
for the \gls{MSRE} pump start-up and coast-down experiments at \gls{ORNL}, which involved control
rod movement, most numerical studies simulate the reactivity effects of the control rods by scaling
the neutron source term by the neutron multiplication factor to keep their reactor model at
criticality \cite{delpech_benchmark_2003, krepel_dyn3d-msr_2007}. Some studies include control rod
models in their steady-state calculations. However, they resort to neutron source term scaling for
the transient calculations due to the inaccuracy of neutron diffusion, $P_1$, and $SP_N$ methods in
highly neutron absorbing regions \cite{kophazi_development_2009, jaradat_development_2021,
yang_development_2022}. Kophazi et al.\ \cite{kophazi_development_2009} modeled annular control rods
as homogenized hexahedrons in their 3-D Cartesian geometry of the \gls{MSRE}. They
homogenized fuel and graphite regions in the rest of the reactor model, as mentioned in Subsection
\ref{sec:msr-tools}. To reduce errors introduced by the neutron diffusion method, they imposed
simple albedo boundary conditions for the thermal neutron group. Jaradat et al.\
\cite{jaradat_development_2021} and Yang et al.\ \cite{yang_development_2022} modeled the
\gls{MSRE} control rods as homogenized wedges in their R-$\theta$-Z mesh due to the constraints of
the nodal neutronics solver. Cui et al.\ \cite{cui_development_2021} also homogenized the control
rods as regular hexahedral nodes in accordance with their nodal solver in Cartesian geometry. A
disadvantage of homogenization-based methods is that it removes some of the heterogeneity in the
flux and temperature. The heterogeneous temperature distribution is especially important in
\glspl{MSR} due to the combined fuel-coolant and the positive temperature reactivity feedback
observed in graphite under certain conditions \cite{mathieu_thorium_2006}.

@@

High-fidelity neutron transport methods fall under two general categories: stochastic Monte Carlo
methods and deterministic methods. Monte Carlo methods involve simulating a finite number of
neutron histories. Randomly generated numbers determine the outcome of various probabilistic events
such as travel distances between particle collisions, types of collisions, and scattering angles in
each history until a neutron capture event terminates it. Deterministic methods for neutron
transport, such as the discrete ordinates $S_N$ and spherical harmonics $P_N$ methods, solve the
\gls{BTE} for neutron transport with some approximations for handling the angular and energy
dependence. The \gls{BTE} for neutron transport is given as:
%
\begin{align}
  \frac{1}{v(E)} \frac{\partial}{\partial t} \Psi(\vec{r},E,\hat{\Omega},&t) + \hat{\Omega}\cdot
  \nabla\Psi(\vec{r},E,\hat{\Omega},t) + \Sigma_t(\vec{r},E,t)\Psi(\vec{r},E,\hat{\Omega},t) 
  \nonumber \\
  - \int^\infty_0 dE'& \int_{4\pi} d\hat{\Omega}' \Sigma_s(\vec{r},E'\rightarrow E,\hat{\Omega}'
  \rightarrow \hat{\Omega},t) \Psi(\vec{r},E',\hat{\Omega}',t) \nonumber \\
  =& \frac{\chi(E)}{4\pi}
  \int^\infty_0 dE' \int_{4\pi} d\hat{\Omega}' \nu\Sigma_f(\vec{r},E',t) \Psi(\vec{r},E',
  \hat{\Omega}',t)+S(\vec{r},E,\hat{\Omega},t) \label{eq:bte}
  \shortintertext{where}
  v(E) =& \mbox{ neutron velocity,} \nonumber \\
  \Psi(\vec{r},E,\hat{\Omega},t) =& \mbox{ neutron angular flux,} \nonumber \\
  \vec{r} =& \mbox{ spatial coordinates,} \nonumber \\
  E =& \mbox{ neutron energy,} \nonumber \\
  \hat{\Omega} =& \mbox{ direction of neutron travel,} \nonumber \\
  t =& \mbox{ time,} \nonumber \\
  \Sigma_t(\vec{r},E,t) =& \mbox{ macroscopic total cross section,} \nonumber \\
  \Sigma_s(\vec{r},E'\rightarrow E,\hat{\Omega}'\rightarrow \hat{\Omega},t) =&
  \mbox{ macroscopic scattering cross section,} \nonumber \\
  \chi(E) =& \mbox{ fission neutron spectrum,} \nonumber \\
  \nu =& \mbox{ number of neutrons produced per fission reaction,} \nonumber \\
  \Sigma_f(\vec{r},E',t) =& \mbox{ macroscopic fission cross section,} \nonumber \\
  S(\vec{r},E,\hat{\Omega},t) =& \mbox{ external neutron source.} \nonumber
\end{align}

@@

\begin{figure}[b!]
    \centering
    \includegraphics[width=.4\columnwidth]{mecs-geometry}
    \caption{Geometries of the absorber region and its vicinity in the supercell
      (top) and the diffusion solver mesh (bottom).
        The shaded and unshaded regions represent the homogenized absorber
        region and the adjacent non-absorber region, respectively.
        Retrieved from Fen et al.\ \cite{fen_modelling_1992}.}
    \label{fig:mecs-geometry}
\end{figure}

Scherer \& Neef developed the \gls{MECS} \cite{scherer_determination_1976} to improve control rod
modeling in \gls{HTGR} with mesh-centered nodal diffusion methods. The \gls{MECS} involves running
a 1-D neutron transport calculation on a representative \textit{supercell} of the heterogeneous
absorber region and its vicinity. The supercell is a volume-preserved model of the absorber region
approximated from its cylindrical or Cartesian geometry in the diffusion calculation. The transport
calculation is typically performed using a fine group structure, fine spatial discretization, and
high-order angular discretization and scattering moments (e.g., $S_8$ method with $P_3$ scattering
matrix) \cite{fen_modelling_1992}. The calculated net neutron leakage rates from the transport
solver are matched with the calculated leakage rates from the diffusion solver according to an
analytic calculation to obtain equivalent diffusion coefficients or cross sections for the absorber
region.

The diffusion coefficient formula for this analytic calculation depends on the solution
method of the diffusion solver. In the most widely used implementation of \gls{MECS} used in
conjunction with the mesh-centered diffusion code CITATION \cite{teuchert_vsop94_1994}, the
diffusion coefficient formula assumes there is only one inner mesh point in the absorber region as
using more inner mesh points dramatically increases the difficulty of finding the proper analytic
formula \cite{fen_modelling_1992}. Other macroscopic cross sections for the absorber region are
calculated using conventional group constant generation techniques from the transport solution
using the supercell average flux and reaction rates. To facilitate further discussion of the
\gls{MECS}, here is an example of applying the \gls{MECS} on a control rod in x-y geometry (Figure
\ref{fig:mecs-geometry}) in the CITATION code as provided by Fen et al.\ \cite{fen_modelling_1992}.

@@

As illustrated by the implementation in CITATION, \gls{MECS} requires considerable user input on
the supercell configuration to ensure that the leakage rates of the transport solution are
equivalent to the leakage rates of the subsequent diffusion solution. This procedure also places
some constraints on the location and size of the absorber node that can be inconsistent with the
nodalization of the rest of the reactor geometry \cite{ougouag_transport_2010}. \gls{MECS} is
incompatible with reactor geometries that contain control rods that are too close to each other
such that there is not enough distance in between to define neighboring nodes where
flux-equivalence is assumed. Lastly, \gls{MECS} is only applicable to coarse-mesh solvers and
homogenizes the control rod along with the adjacent material in its vicinity. Nevertheless,
\gls{MECS} has been widely used within the \gls{VSOP} suite of codes (which contains CITATION) for
\gls{HTGR} neutronic safety analyses
\cite{fen_modelling_1992, reitsma_evaluating_2003, mulder_neutronics_2020}.

@@

In doing so, the Ronen method provides pointwise corrections to the diffusion equation, overcoming
the small flux gradient limitation. Tomatis \& Dall'Osso \cite{tomatis_application_2011}
numerically implemented the Ronen method for a 1-D homogeneous slab with two energy groups and
isotropic scattering. Instead of using Eq. \ref{eq:ronen}, which showed instabilities near flat
flux regions where the denominator approaches zero, they calculated corrections to the diffusion
coefficients at cell interfaces using the difference between the transport- and diffusion-derived
currents as follows:
%
\begin{align}
  \delta D(x_{i+1/2},E) =& -\delta J(x_{i+1/2},E) \frac{(\Delta x_{i+1}+\Delta x_i)/2}{
  \phi(x_{i+1},E)+\phi(x_i,E)} \label{eq:tomatis}
  \shortintertext{where}
    x_i =& \mbox{ $i$-th spatial interval,} \nonumber \\
    \delta J(x,E) =& J_{tr}(x,E) - J_D(x,E), \nonumber \\
    J_D =& \mbox{ diffusion-derived neutron current,} \nonumber \\
    \Delta x_i =& \mbox{ size of $i$-th spatial interval.} \nonumber
\end{align}

@@

As mentioned in Section \ref{sec:summary-nts-mtds}, coarse-mesh and nodal methods homogenize
heterogeneities in reactor geometries to reduce the computational costs of running full-core
simulations. Equivalence techniques that reduce spatial homogenization error are also effective
for accurately modeling the integral worths of control rods within fuel assemblies. The \gls{GET}
\cite{koebke_new_1980, smith_nodal_1983} and \gls{SPH} \cite{kavenoky_sph_1978,
hebert_consistent_1991} methods represent the most widely used equivalence methods for improving
the performance of diffusion calculations in homogenized \gls{LWR} models. Both methods involve
deriving additional homogenization parameters from single-assembly transport calculations with
reflective boundary conditions. Since the transport calculation step is already a prerequisite
for generating homogenized group constants, the equivalence methods are simple to implement and
impose reasonably small additional computational costs.

@@

The \gls{GET} and the \gls{SPH} methods are designed to preserve reaction rates at the assembly
level \cite{yamamoto_cell_2004}. Given that the \gls{SPH} method introduces only one correction
factor per cell, it only preserves the average net current across all surfaces as opposed
to the net current at each surface with \gls{GET}. Similarly, the isotropic nature of \gls{SPH}
factors leads to worse pin-power estimates near control rods and reflectors compared to \gls{GET}.
However, the \gls{SPH} method is simpler to implement in the diffusion solver as the \gls{SPH}
factors can be precombined with the cross sections to generate \gls{SPH}-corrected cross sections.
\gls{GET} requires diffusion solvers that allow for flux discontinuities at the interfaces.
Furthermore, \gls{GET} requires more memory to store up to six discontinuity factors, one for each
mesh surface, in 3-D calculations.

@@

Lastly, there is a lack of existing work into robust techniques for accurate control rod modeling
for time-dependent \gls{MSR} analyses. Control rods induce highly anisotropic fluxes within
themselves and their vicinities that the neutron diffusion approximation cannot model accurately.
Inaccurate rod worth estimates subsequently affect transient reactor power and temperature
distribution calculations. Higher-fidelity neutron transport methods remain too computationally
expensive for time-dependent multiphysics \gls{MSR} simulations. However, transport-correction
techniques can be applied to augment neutron diffusion calculations in these regions. While few
have been applied to \gls{MSR} multiphysics simulations other than albedo boundary conditions,
various techniques have been proposed and implemented for other reactor types. Helpful information
may be gleaned from these techniques to improve control rod modeling in \glspl{MSR} with the
neutron diffusion method.

### 2025-01-03 main.tex
Edits before format review

%\title{A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors}
\title{Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling}
\author{Sun Myung Park}
\department{Nuclear, Plasma \& Radiological Engineering}
\degreeyear{2024}
\committee{Associate Professor Kathryn D. Huff, Co-Chair \\
           Assistant Professor Madicken Munk, Co-Chair \\
           Professor Rizwan Uddin \\
           Professor Tomasz Kozlowski \\
           Professor Paul Fischer}

@@

%\input{acks}

>>>>

%\title{A Hybrid Neutronics Method for Time-Dependent Control Rod Modeling in Molten Salt Reactors}
\title{Advancements in Moltres for Time-Dependent Multiphysics Molten Salt Reactor Modeling}
\author{Sun Myung Park}
\department{Nuclear, Plasma \& Radiological Engineering}
\degreeyear{2024}
\committee{Associate Professor Kathryn D. Huff, Co-Chair \\
           Assistant Professor Madicken Munk, Co-Chair, Oregon State University \\
           Professor Rizwan Uddin \\
           Professor Tomasz Kozlowski \\
           Professor Paul Fischer}

@@

\input{acks}
